Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-01-22 paper.tex
Edit abstract.

\title{Minimax lower bounds for source localization}

@@

The ``source localization'' problem is one that arises in several fields. For
instance, in neuroscience, one might wish to use electroencephalography (EEG)
measurements to locate the source of brain activity.
\textcolor{red}{<Briefly mention other applications>}.

The common underlying factor in each of these problems is the presence of a
point source, whose signal passes through a diffusive medium and is sensed by
an array of sensors. We then wish to recover the location of the source using
noisy sensed values. The diffusive medium is modeled as acting like a low-pass
filter. The noise is taken to be additive gaussian noise \textcolor{red}{which
may have a non-diagonal covariance matrix}.

\textcolor{red}{Rephrase this para.}
We give minimax lower bounds on the squared error in estimating the location of
the source, which applies to all estimators, when using unformly distributed
sensors and for certain classes of impulse response of the low-pass filter. Our
bounds are the first to give a scaling in terms of sensor density.

>>>>

\title{Lower Bounds on the Minimax Risk for the \\ Source Localization Problem}

@@

The ``source localization'' problem is one in which we wish to estimate the
location of a point source observed through a diffusive medium using an array
of sensors. The diffusive medium is modeled as a low-pass filter, and the noise
is taken to be additive, white and gaussian.

We give lower bounds on the minimax risk (mean squared-error in location) in
estimating the location of the source, which applies to all estimators, for
\textcolor{red}{compactly supported (am I using this correctly?)} Lipschitz-continuous impulse responses of
the low-pass filter, when using a unformly distributed sensor array. We show
that the minimax error decays to zero inversely in the number of sensors. We
also perform a preliminary numerical analysis for a more physical model that
views sensors as integrators, wherein the bound saturates before going to zero
for large sensor numbers. The benefit of increased sensor density is seen only
when the signal-to-noise ratio is high. Our bounds are the first to give a
scaling in terms of the number of sensors used.

While our results are shown for sources located on a one-dimensional circular
domain, they can be easily extended to sources on one-dimensional line segments
and d-dimensional boxes. The technique for deriving these minimax bounds also
sheds light on the sensor placement problem: increased resolution in a narrow
region can be obtained by placing sensors \emph{around} the region of interest.
